Enhancing Urban Building Simulations in HiDALGO2 through CI/CD Innovations

### 2024-05-26 hid2-urban-building-cicd.tex
new figures, added captions and updated text

In the figure~\ref{fig:buildings}, we illustrate the different levels of details.

\begin{figure}[htbp]
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod0.png}
  \caption{LOD-0}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod1.png}
  \caption{LOD-1}
  \label{fig:sub2}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod2.png}
  \caption{LOD-2}
  \label{fig:sub3}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
  \caption{LOD-2 with a zoom}
  \label{fig:sub4}
\end{subfigure}
\caption{}
\label{fig:buildings}
\end{figure}

@@

In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0~\ref{fig:city-strasbourg-lod0} and LOD-1\ref{fig:city-strasbourg-lod1} representations.

@@

The Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPC-ops workflow
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/feelpp-hpcops.png}
    \caption{CI/CD HPC-ops for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\section{Conclusion}
The CI/CD practices in Feel++ not only enhance the development lifecycle of the framework itself but also ensure that all dependent projects maintain high standards of reliability, security, and performance. The integration of Docker and Apptainer into the workflow enables wide-ranging deployment scenarios from personal computing environments to high-performance computing clusters.

>>>>

In the figure~\ref{fig:buildings}, we illustrate the different levels of details. Panel~\ref{fig:building-lod0} displays the LOD-0 of a building with its bounding box.
Panel~\ref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM.

\begin{figure}[htbp]
\centering
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod0.png}
  \caption{LOD-0: a building is represented by its bounding box}
  \label{fig:building-lod0}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod1.png}
  \caption{LOD-1: a building is represented by its ground footprint elevated to its height}
  \label{fig:building-lod1}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod2.png}
  \caption{LOD-2: a building in full detail using BIM. Note that LOD-2 and LOD-1 are mixed.}
  \label{fig:building-lod2}
\end{subfigure}%
\begin{subfigure}{.4\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/buildings-lod2-zoom.png}
  \caption{LOD-2: A zoom on the LOD-@ building.}
  \label{fig:building-lod2-zoom}
\end{subfigure}
\caption{Different representations of a building using our LOD definition}
\label{fig:buildings}
\end{figure}

@@

In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPC-ops workflow for Feel++. The Urban Building 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/feelpp-hpcops.png}
    \caption{CI/CD HPC-ops for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/ub-devops.pdf}
    \caption{Urban Building standard Devops}
    \label{fig:ub-devops}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{images/ub-hpcops.pdf}
    \caption{Urban Building HPC Ops workflow}
    \label{fig:ub-hpcops}
\end{figure}
\section{Conclusion}
The CI/CD practices in Feel++ not only enhance the development lifecycle of the framework itself but also ensure that all dependent projects maintain high standards of reliability, security, and performance. The integration of Docker and Apptainer into the workflow enables wide-ranging deployment scenarios from personal computing environments to high-performance computing clusters.
